---
title: "p8105_hw1_xc2859"
author: "Xiaoxue Cui"
date: "2026-09-24"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


# Problem 1

Load the penguins dataset. 

```{r}
data("penguins", package = "palmerpenguins")
```

Dataset description: 

The `penguins` dataset contains 8 important variables: `r names(penguins)`. 

The categorical variables include: 
`species` (Adelie, Chinstrap, and Gentoo), 
`island` (Biscoe, Dream, and Torgersen), and 
`sex` (female and male).  
The numeric variables include: 
`bill_length_mm` (range from `r range(penguins$bill_length_mm, na.rm = TRUE)` mm), 
`bill_depth_mm` (range from `r range(penguins$bill_depth_mm, na.rm = TRUE)` mm), 
`flipper_length_mm` (range from `r range(penguins$flipper_length_mm, na.rm = TRUE)` mm), 
`body_mass_g` (range from `r range(penguins$body_mass_g, na.rm = TRUE)` g), and
`year` (study year of 2007, 2008 and 2009). 

The dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. 