---
title: "p8105_hw1_xc2859"
author: "Xiaoxue Cui"
date: "2026-09-24"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANGUAGE = "en")
```


# Problem 1

__Load the penguins dataset__

```{r}
data("penguins", package = "palmerpenguins")
```

__Describe the dataset__ 

The `penguins` dataset contains 8 important variables: `r names(penguins)`. 

The categorical variables include: 
`species` (Adelie, Chinstrap, and Gentoo), 
`island` (Biscoe, Dream, and Torgersen), and 
`sex` (female and male).  
The numeric variables include: 
`bill_length_mm` (range from `r range(penguins$bill_length_mm, na.rm = TRUE)` mm), 
`bill_depth_mm` (range from `r range(penguins$bill_depth_mm, na.rm = TRUE)` mm), 
`flipper_length_mm` (range from `r range(penguins$flipper_length_mm, na.rm = TRUE)` mm), 
`body_mass_g` (range from `r range(penguins$body_mass_g, na.rm = TRUE)` g), and
`year` (study year of 2007, 2008 and 2009). 

The dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. 

__Draw a scatterplot of `flipper_length_mm` vs. `bill_legnth_mm`__

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

ggplot(penguins, 
       aes(x = bill_length_mm, y = flipper_length_mm, color = species)
) + geom_point()

ggsave("penguin_scatterplot.png")
```




# Problem 2

__Create a data frame__

```{r}
data_df = tibble(
  norm_samp = rnorm(10), 
  logical_vec = norm_samp > 0, 
  chara_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"), 
  factor_vec = factor(
    c("level 1", "level 2", "level 3", "level 1", "level 2", "level 3", "level 1", "level 2", "level 3", "level 1"))
)

data_df
```

The created data frame contains a random sample of size 10 from a standard Normal distribution (`norm_samp`), a logical vector indicating whether elements of the sample are greater than 0 (`logical_vec`), a character vector of length 10 (`chara_vec`), and a factor vector of length 10 (`factor_vec`), with 3 different factor “levels” (level 1, level 2, and level 3). 

__Take the mean of each variable__

```{r}
mean(pull(data_df, norm_samp))
mean(pull(data_df, logical_vec))
mean(pull(data_df, chara_vec))
mean(pull(data_df, factor_vec))
```
The mean can be calculated for only 2 variables, `norm_samp` and `logical_vec`. `norm_samp` is a numeric variable and we can naturally get its mean. `logical_vec` is a logical variable, and R treats the `TRUE` result as 1 and `FALSE` result as 0, so its mean represents the proportion of observations that are `TRUE`. Therefore, we can calculate the means for these two variables. 

However, we cannot get the means of `chara_vec` and `factor_vec` because they are not numeric or logical variables. 
